---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# caples

Fast, plain-English readouts for A/B/n tests on conversion rates.

Named after John Caples, who pioneered tested advertising.

## Installation

```r
# install.packages("remotes")
remotes::install_github("RobinMahachi/caples")
```

## Workflow

Plan first, analyse second.

```{r example}
library(caples)

# 1. Plan the test before it runs
plan <- caples_design(baseline = 0.05, mde = 0.01, power = 0.85, arms = 3)
plan

# 2. Run the test (simulated here)
set.seed(42)
n <- plan$n_per_arm
df <- data.frame(
  arm = rep(c("control", "A", "B"), times = n),
  converted = c(rbinom(n[1], 1, 0.050),
                rbinom(n[2], 1, 0.052),
                rbinom(n[3], 1, 0.062))
)

# 3. Read it out against the plan
caples_test(df, group = "arm", outcome = "converted",
            ctrl = "control", design = plan)
```

## What it does

- Sizes tests with equal or unequal traffic splits and multiple arms
- Pooled two-proportion z-tests with multiplicity correction (Holm by default)
- Absolute and relative lifts with confidence intervals
- Sample ratio mismatch (SRM) check
- Sample size vs plan, and the achieved minimum detectable effect
- A plain-English summary for stakeholders